\chapter{Overview of the Theory of HYPERION}

\subsection{Overview of the Instrumental Design}

Let us now consider the design of our interferometer itself. There are two key 
areas of interest to us: how our sensitivity to the monopole varies with the 
separation between antennas, and how it changes in the presence of different 
absorber structures and materials. Another way of viewing it would be: how do 
the characteristics of the individual elements and of the array design affect 
our ability to make this measurement.

Let us first consider the array design, i.e. baseline separations. For this 
simulation, we import a model array using the AIPy AntennaArray framework, 
which enables us to carry around an array with known geometry and baseline 
separations, along with individual antenna beam patterns and accessible 
frequencies. With this information and the previously made sky maps, we are now 
able to calculate our visibilities across many frequencies by using 
Eq.~\eqref{eq:vis}.

Intuitively, we expect that the sensitivity to the global signal will be 
maximized with the smallest baseline separations, which correspond to a 
position in the \emph{uv}-plane close to the origin, or the zero-spacing mode.  
The trade-off of this, from a design perspective, comes in the difficulty of 
ameliorating cross-talk in a densely packed array. We want to optimize our 
array design to space our antennas as loosely as possible while also 
maintaining workable sensitivity to the monopole term, as this will best enable 
us to mitigate systemic problems in our instrument and perform a successful 
experiment.

The AntennaArray framework also enables us to carry around models of the beams 
of the antennas, which is a convenient way to import absorbers into the 
simulation. Essentially, within the context of the simulation, the absorbers 
act as a modification term on the beam pattern, changing the way that each 
individual antenna sees the sky. This works as follows:

To start, we need a beam. HYPERION uses SARAS-style fat dipole antennas in our 
instrument, which means we will be using a frequency-invariant dipole beam 
pattern in our simulation to match~\citep{patra2013}. This is the base beam 
model used throughout the simulation, calculated using 
Eq.~\eqref{eq:dipole-beam}.

\begin{equation}
    \label{eq:dipole-beam}
    A(\theta, \phi, \nu) = \cos\Big(\frac{\frac{\pi}{2} 
    \cos{\theta}}{\sin{\theta}}\Big)
\end{equation}

The next step is to add the absorber, which we do via modification of the AIPy 
Antenna beam. The absorber structure in our simulation is essentially a 
cylindrical wall of uniform height centered around each antenna, so that the 
antenna sees a rotationally symmetric structure. The parameters we can play 
with are the absorptivity of the material (i.e. how much attenuation does the 
absorber provide at each frequency), the height of the absorber walls, and how 
smooth the transition from absorber to sky is. This calculation is done using 
Eq.~\eqref{eq:absorber-baffle},

\begin{equation}
    \label{eq:absorber-baffle}
    B(\theta, \phi, \nu) = \Big[10^{\alpha(\nu)/20} \Big(\frac{1}{2} + 
    \frac{1}{2} \tanh\Big(\frac{\theta - (\frac{1}{2} - 
    \theta_{0})}{a}\Big)\Big) + \Big(1 - \Big(\frac{1}{2} + \frac{1}{2} 
    \tanh\Big(\frac{\theta - (\frac{1}{2} - \theta_{0})}{a}\Big)\Big)\Big)\Big]
\end{equation}

where $\alpha(\nu)$ is the absorptivity by frequency of the absorber, 
$\theta_0$ is the cutoff angle of the structure (i.e. $\theta_0$ is the height 
of the absorber walls), and $a$ is the smoothing parameter that blends the 
transition between the absorber and the sky.

This term is then combined with the Antenna beam, giving us 
Eq.~\eqref{eq:absorber-beam}.

\begin{equation}
    \label{eq:absorber-beam}
    A'(\theta, \phi, \nu) = A(\theta, \phi, \nu) B(\theta, \phi, \nu)
\end{equation}

\subsection{Calculating Visibilities by Baseline Separation}

One of the fundamental constructs of the theory of astronomical interferometry 
is that samples spatial variance on the sky. Interferometers, by nature, are 
not designed to observe global light sources. Rather, interferometers excel at 
observing differences -- a star or other point source will have light in one 
place and no light everywhere else, galaxies will have clumpy, fluffy light in 
some places but not all places. The interferometer can be built and designed to 
observe some scales better than others, and can tease out these differential 
light sources with great success.

So one might reasonably be surprised to hear that we are taking an 
interferometer and trying to do the one exact thing that it is, theoretically, 
unequipped to handle: trying to observe a global average phenomenon on the sky.


