% For a masters thesis, replace the above \documentclass line with
% \documentclass[masters]{ucbthesis}
% This affects the title and approval pages, which by default calls this
% document a "dissertation", not a "thesis".

\documentclass[masters]{ucbthesis}

% support display of graphics
\usepackage{graphicx}

% import library of technical symbols
\usepackage{amsmath,amssymb,latexsym}

% import bibliography tools
\usepackage{natbib}
\citestyle{aa}

% To compile this file, run "latex thesis", then "biber thesis"
% (or "bibtex thesis", if the output from latex asks for that instead),
% and then "latex thesis" (without the quotes in each case).

% Double spacing, if you want it.  Do not use for the final copy.
% \def\dsp{\def\baselinestretch{2.0}\large\normalsize}
% \dsp

% If the Grad. Division insists that the first paragraph of a section
% be indented (like the others), then include this line:
% \usepackage{indentfirst}

\begin{document}

% Declarations for Front Matter

\title{HYPERION: The Case for Interferometry in 21 cm Reionization Global 
Signal Studies}
\author{Kara Kundert}
\degreesemester{Fall}
\degreeyear{2018}
\degree{Master of Astrophysics}
\chair{Professor Aaron Parsons}
\othermembers{Professor Martin White \\
  Professor Eugene Chiang}
\numberofmembers{3}
\field{Astronomy}
\campus{Berkeley}

\maketitle
% Delete (or comment out) the \approvalpage line for the final version.
\approvalpage
\copyrightpage

\include{abstract}

\begin{frontmatter}

\begin{dedication}
\null\vfil
\begin{center}
 \noindent{\large{\emph{Failure is simply the opportunity to begin again,\\ 
 this time more intelligently.}}\\ \normalsize{-- Henry Ford}}
\end{center}
\vfil\null
\end{dedication}

% You can delete the \clearpage lines if you don't want these to start on
% separate pages.

\tableofcontents
\clearpage
\listoffigures
\clearpage
%\listoftables

\begin{acknowledgements}
 This work would not have been possible without the financial support of the 
 National Science Foundation CAREER Award, the International House Carl \& 
 Betty Helmholz Gateway Fellowship, or the University of California, Berkeley 
 Department of Astronomy. 

 I must also give ample thanks to those with whom I have had the pleasure of 
 working on this and related projects. In particular, I would like to thank 
 Cherie Day, who has given me her love, her support, and her valuable 
 scientific and engineering insights since my first day on the Berkeley campus.  
 I would also like to thank the past and present members of the HYPERION team, 
 including Nipanjana Patra, Sanah Bhimani, Trisha Bhattacharya, Daniel Shen, 
 Raj Biswas, and Liju Phillip. Their hard work, patience, and, at times, upper 
 body strength, have made this project what it is today.  I could not have 
 reached this point without their combined abilities, and I am endlessly 
 grateful for their contributions.

 I would also like to thank the various members of the department who have 
 helped me along the path to completing this thesis. To Fatima Abdurrahman, 
 thank you for the dumplings and your friendship. To Charles Goullaud, thank 
 you for letting me unload my stress over some of your very fine whiskey and 
 some very silly movies. To Deepthi Gorthi, thank you for walking with me when 
 I needed to get out of the department and get some perspective. To Tom Zick, 
 Carina Cheng, and Zaki Ali, thank you for stepping in and providing me with 
 support when I most needed it.

 I am so grateful to my friends outside of the department, who have been 
 endlessly and creatively supportive along this journey. To Tristan Scroggins, 
 thank you for believing in me when I did not. To Tj Carskadon, thank you for 
 always being there for me, no matter whether I need career advice, a study 
 buddy, a drinking partner, a pep talk, or a hug.  To Cameron Chalker, thank 
 you for not listening to my excuses and always driving me to give my best, and 
 for reminding me of the consequences of reneging on our long-standing deal.

 Finally, I cannot adequately express how grateful I am to my father. He has 
 always been my greatest ally and continues to support me in every way he can. 
 I would not have been able to complete this thesis without him standing 
 steadfastly in my corner.

\end{acknowledgements}

\end{frontmatter}

\pagestyle{headings}

\include{chap1}
\include{chap2}
\include{chap3}
\include{chap4}
\include{chap5}
\include{conclusion}

\appendix
\include{appendix}

\bibliography{references}{}
\bibliographystyle{apj}

%\printbibliography

\end{document}
